%کلمات کلیدی انگلیسی
\latinkeywords{Predictive Maintenance, Vibration Analysis, Machine Learning, Internet of Things}
%چکیده انگلیسی

\en-abstract{
The success of the Internet of Things depends on our ability to solve challenging problems that were previously impossible. One of the most critical challenges in the IoT space is preventive maintenance in industrial manufacturing processes to maximize equipment availability and durability. Traditionally, preventive management has followed only lower-cost strategies, such as time-based or utilization-based management. With the large amount of sensor data collected from the Internet of Things, we can develop much smarter predictive maintenance based on the accurate prediction of machinery failure. In this project, we have developed a system consisting of a core server and a machine learning package based on vibration sensor data to implement predictive maintenance. More precisely, we advanced the process of building a machine learning model based on the pre-processing of sensor data, extracting suitable features and then analyzing these features. Finally, by learning a linear model based on the analysis and comparison of these features with healthy devices, we predicted the remaining useful time for each existing node. By using such a system in the industry, maintenance costs as well as possible losses incurred will be greatly reduced.
}
%%%%%%%%%%%%%%%%%%%%% کدهای زیر را تغییر ندهید.

\newpage
\thispagestyle{empty}
\begin{latin}
\section*{\LARGE\centering Abstract}

\een-abstract

\vspace*{.5cm}
{\large\textbf{Key Words:}}\par
\vspace*{.5cm}
\elatinkeywords
\end{latin}